SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-22 Chapters/sdm-autocorrelation.tex
SDM Autocorrelation typo.
recompiling..

This is an important observation. A hard location is activated because it shares many dimensions with the items read from or written onto it. Imagine the `counter's eye view':  each individual counter `likes'\footnote{If you are a cell I then I have some serious piece of advice to you.  I would strongly suggest avoiding the neighborhood of a neuron. Neurons have serious authoritarian tendencies, bossing around --- generally electrifying --- the hopeless innocent cells around them just because.} to write on its own corresponding bit-address value more than it likes the opposite; as each hard-location has a say in its own area --- and nowhere else.

>>>>

This is an important observation. A hard location is activated because it shares many dimensions with the items read from or written onto it. Imagine the `counter's eye view':  each individual counter `likes' to write on its own corresponding bit-address value more than it likes the opposite; as each hard-location has a say in its own area --- and nowhere else.

%\footnote{If you are a cell I then I have some serious piece of advice to you.  I would strongly suggest avoiding the neighborhood of a neuron. Neurons have serious authoritarian tendencies, bossing around --- generally electrifying --- the hopeless innocent cells around them just because.}
